Descriptions of four new species of \textit{Minyomerus} Horn, 1876 (Coleoptera: Curculionid\ae), with notes on their distribution and phylogeny

### 2018-03-04 tex/manuscript.tex
Added checklist and finalized cladistics

\section*{Introduction}
	The weevil genus \textit{Minyomerus} Horn, 1876 is currently assigned to the tribe Tanymecini Lacordaire, 1863 (Curculionidae: Entiminae). 
	The genus was recently revised and includes a total of 17 described species distributed throughout the desert and plains regions of North America.
	Since the publication of the monographic revision of \textit{Minyomerus}, we have discovered four additional undescribed species, known to us only from limited numbers of specimens, yet falling neatly into the generic delimitation of \textit{Minyomerus} \textit{sensu} Jansen and Franz 2015.
	Here we describe these species and provide images of the holotypes and of dissected genitalia for the purpose of identification.
	We additionally conduct a morphological phylogenetic analysis of the genus to clarify the placement of these new taxa within \textit{Minyomerus}, based on the analysis provided in our previous work.
	An emended identification key to the species of \textit{Minyomerus} is given along with information on the geographic distribution of the herein described species.
	Where possible, we make note of host-plant records and briefly consider the historical biogeographic relationships of the new species.
	A more extensive discussion of the habits, distribution, and delimitation of the genus (and all of its constituent species) can found in the generic revision.

\section*{Materials and methods}
	The keen reader will note a certain similarity between the methods used in this manuscript with those of Jansen and Franz 2015. 
	Rather than merely referencing the monograph as a source of inspiration, we feel it is better to provide a fully transparent and updated accounting of the methods used to generate the species descriptions, distribution maps, and phylogeny herein.
	Most notably, we retain the format of the species descriptions, whereby we emphasize only those characters that vary significantly from the generic description, as explained below.
	\paragraph{Natural history observations} 
		Members of the genus \textit{Minyomerus} may be found on a variety of host plants, as indicated following each description.
		While many species appear to be generalists, the adults are consistently observed on the leaves and branches of the host feeding on the leaf tissue; all other life stages remain unknown.
		Members of this genus are commonly found in deserts throughout western North America, including the Mojave, Sonoran, Chihuahuan, and Great Basin Deserts. 
		Furthermore, the range of the genus extends through the semi-arid regions of the Great Plains, the Colorado Plateau, and Baja California, Mexico. 
		The adults are flightless, as the hind wings and associated flight structures of all species are either greatly reduced or not readily apparent in dissection.

@@

		Herein recognized species of \textit{Minyomerus}  were delimited through application of the phylogenetic species concept \textit{sensu} Wheeler and Platnick (2000).
		Species descriptions are in alphabetical order, rather than phylogetic order, for ease of use.
		The species descriptions in this manuscript represent unique and complementary accounts of the character states observed in each species, including their variability, but except those characters invariant within the genus as specified in the higher-level description of \textit{Minyomerus}.
		Likewise, descriptions of males emphasize characters that are variable and sufficiently different from those of the females to merit recognition.
		The key to identifying species of \textit{Minyomerus} is arranged with emphasis being placed on the most readily observable diagnostic characters.
		This manuscript is arranged with the species descriptions appearing first, followed by the key to species, and then by the phylogenetic results.

	\paragraph{Phylogenetic analysis}
		The morphological cladistic analysis includes 26 terminal taxa; with 21 ingroup and 5 outgroup terminals.
		Following resolution of species identities and boundaries, the ingroup terminals were represented by six species previously assigned to Minyomerus sec. O’Brien and Wibmer (1982), Piscatopus griseus sec. Sleeper (1960), and ten newly recognized species.
		The lack of prior phylogenetic analyses of Minyomerus and closely related lineages made it necessary to sample outgroups fairly broadly while remaining focused on North American lineages that are are putative close relatives of the ingroup (Nixon and Carpenter 1993).
		The tribe Tanymecini [non-focal] is cosmopolitan, with the subtribe Tanymecina [non-focal] containing the majority of New World species diversity in the tribe (Alonzo-Zarazaga and Lyal 1999).
		Accordingly, four outgroup terminals are represented by species belonging to separate genera in the Tanymecina [non-focal]; viz. Pandeleteius cinereus (Horn, 1876) [non-focal], Pandeleteinus subcancer Howden, 1969 [non-focal], Isodrusus debilis Sharp, 1911 [non-focal], and Isodacrys buchanani Howden, 1961 [non-focal].
		Because generic relationships in the Tanymecini [non-focal] remain unresolved, it was deemed prudent to find a relatively far-removed taxon to root the cladogram that would nevertheless display states that are applicable to the ingroup for all characters under consideration (Rieppel 2007; Franz 2014).
		For this purpose we select the North American species Sitona californicus (Fahraeus, 1840) [non-focal], representing the tribe Sitonini Gistel, 1856 [non-focal].
		The character matrix was edited and phylogenetic results reviewed and reconnected to the input using the WinDada and WinClados interfaces of WinClada (Nixon 2002).
		The character sequence follows that of the taxonomic descriptions.
		The most parsimonious tree and character state optimizations were inferred under parsimony using NONA (Goloboff 1999).
		An unconstrained heuristic search of tree space for the 22-terminal matrix was conducted using the commands: hold 100001, mult*1000, hold/100, with mult*max* selected.
		Bootstrap support was inferred in WinClada using the parameters of 1000 replications, hold 1000, hold/100, mult*10, “Don’t do max*”, and “Save consensus”.
		Finally, Bremer support values (Bremer 1994) were calculated in NONA using the commands hold 20000, suboptimal 20, and bsupport 20.
	\paragraph{Species distribution modeling}
		We used the modeling program Maxent, Version 3.4, to generate habitat models for the species of Minyomerus [JF 2015] (Figs 50–52) based on the documented occurrence records (Phillips et al. 2004, 2006; Elith et al. 2011).
		The default settings “Max number background points”, set to 100,000, and “Iterations” set to 10 and with cross-validation, were applied to leverage all available locality data.
		However, no models could be created for one species a single documented locality.
		We selected 19 bioclimatic variables and elevation as Environmental Layers in Maxent, obtained from WorldClim (see Hijmans et al. 2005 and the associated website for further detail on variables).
		The layers were downloaded by tile (zones 11–13 and 21–23), with a 30 arc-second resolution (projected using WSG 84) to provide adequate coverage of the full distribution of Minyomerus [JF2015].
		These tiles were assembled, by layer, into composite maps of six tiles each, using QGIS, Version 2.8.1 ‘Wien’, prior to species distribution modeling (Quantum GIS Development Team 2015).
		After modeling, the raster files of the predictive probabilities were imported into GIS.
		Each file was designated a specific color, and each pixel in the raster grid was assigned a linearly interpolated saturation of that color, with increasing saturation denoting an increased probability of successful prediction of species presence at that point.
		Pixels with a value below 0.50 were rendered transparent so that the model only shows regions with a greater than 50\% chance of successful prediction.
		The raster files were clipped to remove extraneous predicted regions based on: (1) predictive probability (i.e., removing large areas with only transparent pixels) and (2) geographic extent (accounting for endemicity).
		For instance, species endemic to Baja California Sur, Mexico, do not require a predictive model for bioclimatically similar habitats in Canada.
		The actual (documented) occurrence records are laid over the modeled habitat ranges as colored circles on the respetive maps (Figs 50–52), along with vector layers of country and state borders (Hijmans et al. 2012).

@@

			\#

@@

			\paragraph{Manidbles}

@@

				Protibia/profemur length ratio \#; protibial apex with ventral setal comb recessed in an incurved groove; mucro present as a large, black, sub-triangular, medially-projected tooth, which is approximately equilateral and whose sides are subequal in length to surrounding setae. 

@@

				Length/width ratio \#; widest at anterior 1/3; anterior margins jointly 1.75\x wider than posterior margin of pronotum and strongly produced dorsally from margin of pronotum; lateral margins evenly rounded until posterior 1/3, more strongly rounded and converging thereafter. 

@@

				Comma-shaped; collum expanded to form a long, cylindrical projection, subequal in length to ramus, 1/3\x width of corpus, angled at 45\td to corpus, apically with a reduced hood-shaped projection; ramus elongate, bulbous, slightly wider than thickness of corpus, basally constricted to form a short stalk; corpus not greatly swollen; cornu sub-equal in length to corpus and collum, recurved distally to form in inner angle of 60\td to corpus, straight and gradually narrowing along basal 2/3, with apical 1/3 abruptly narrowed, angled at 45\td to coprus, and tapering to a slight knob.

@@

			\#

@@

			The label indicates "Geococcyx calif"; this is presumably a reference to \textit{Geococcyx californianus} (Lesson, 1829) [Cuculidae], the Greater Roadrunner, although it is unclear if the specimen was found on or near one of these birds (either living, dead, or in a nest).

@@

			\#

@@

				Protibia/profemur length ratio \#; protibial apex with ventral setal comb recessed in a subtly incurved groove; mucro present as a large, black, sub-triangular, medially-projected tooth, which is approximately equilateral and whose sides are subequal in length to surrounding setae. 

@@

				Length/width ratio \#; widest at anterior 1/3-1/4; anterior margins jointly 1.5\x wider than posterior margin of pronotum; lateral margins subparallel to slightly rounded after anterior 1/3, more strongly rounded and converging in posterior 1/3. 

@@

			\#

@@

@@

			\#

@@

@@

				Stipes subrectangular, 1.5\x wider than long, roughly equal in width to inner arm of bifurcation of cardo, glabrous. 

@@

				Rostrum ventrally with subparallel sulci beginning at corners of oral cavity and continuing halfway to back of head.

@@

				Pronotum in lateral view with transverse ventrolateral sulci strongly excavated and distinctly sculptured; with short, recumbent to suberect setae that barely attain or reach just beyond anterior margin; these setae becoming shorter and more erect laterally, reaching a maximum length nearly equal to length of eye; dorsally, these setae become uniquely apically explanate, with a longitudinal, medial, ridgelike portion that tapers to either side apicolaterally.

@@

				Length/width ratio \#; widest at anterior 1/6; anterior margins jointly 1.5-2\x wider than posterior margin of pronotum; lateral margins nearly straight and subparallel after anterior 1/5, converging in posterior 1/3. 

@@

			\#

@@

\section*{Checklist of species}
	\#
\section*{Identification key}
	\#
\section*{Phylogenetic placement of new species}
	\#
\section*{Acknowledgments}

>>>>

\section*{Introduction}
	The weevil genus \textit{Minyomerus} Horn, 1876 is currently assigned to the tribe Tanymecini Lacordaire, 1863, subtribe Tanymecina Lacoirdaire, 1863 (Curculionidae: Entiminae). 
	The genus was recently revised and includes a total of 17 described species distributed throughout the desert and plains regions of North America.
	Since the publication of our monographic revision of \textit{Minyomerus}, we have discovered four additional undescribed species, known to us only from limited numbers of specimens, yet falling neatly into the generic delimitation of \textit{Minyomerus} \textit{sensu} Jansen and Franz 2015.
	Here we describe these species and provide images of the holotypes and of dissected genitalia for the purpose of identification.
	We additionally conduct a morphological phylogenetic analysis of the genus to clarify the placement of these new taxa within \textit{Minyomerus}, based on the analysis provided in our previous work.
	An emended identification key to the species of \textit{Minyomerus} is given along with information on the geographic distribution of the herein described species.
	Where possible, we make note of host-plant records and briefly consider the historical biogeographic relationships of the new species.
	A more extensive discussion of the habits, distribution, and delimitation of the genus (and all of its constituent species) can found in the generic revision.

\section*{Materials and methods}
	The keen reader will note the alignment of the methods used in this manuscript with those of Jansen and Franz 2015. 
	For convenience and transparency, we provide an updated account of the methods used to generate the species descriptions, distribution maps, and phylogeny herein.
	Most importantly, we retain the format of the species descriptions, whereby we emphasize only those characters that vary significantly from the generic description, as explained below.

	\paragraph{Natural history observations} 
		Members of the genus \textit{Minyomerus} may be found on a variety of host plants, as indicated following each description.
		While many species appear to be generalists, the adults are consistently observed on the leaves and branches of the host feeding on the leaf tissue; all other life stages remain unknown.
		Members of this genus are commonly found in deserts throughout western North America, including the Mojave, Sonoran, Chihuahuan, and Great Basin Deserts. 
		Furthermore, the range of the genus extends through the semi-arid regions of the Great Plains, the Colorado Plateau, and Baja California, M\'{e}xico. 
		The adults are flightless, as the hind wings and associated flight structures of all species are either greatly reduced or not readily apparent in dissection.

@@

		Herein recognized species of \textit{Minyomerus}  were delimited through application of the phylogenetic species concept \textit{sensu} Wheeler and Platnick (2000).
		Species descriptions are in alphabetical order, rather than phylogetic order, for ease of use.
		The species descriptions in this manuscript represent unique and complementary accounts of the character states observed in each species, including their variability, but excepting those characters invariant within the genus as specified in the higher-level description of \textit{Minyomerus}.
		Likewise, descriptions of males emphasize characters that are variable and sufficiently different from those of the females to merit recognition.
		The key to identifying species of \textit{Minyomerus} is arranged with emphasis being placed on the most readily observable diagnostic characters.
		This manuscript is arranged with the species descriptions appearing first, followed by the key to species, and then by the phylogenetic results.

	\paragraph{Phylogenetic analysis}
		The morphological cladistic analysis includes 26 terminal taxa; with 21 ingroup and 5 outgroup terminals.
		The ingroup terminals were represented by 17 species previously assigned to \textit{Minyomerus} sec. Jansen and Franz (2015) and four newly recognized species.
		In keeping with our previous analysis, we sampled outgroups fairly broadly while remaining focused on North American lineages that are putative close relatives of the ingroup (Jansen and Franz 2015, Nixon and Carpenter 1993).
		Although the tribe Tanymecini [non-focal] is cosmopolitan, the majority of New World species diversity in the tribe may be found in the subtribe Tanymecina [non-focal] (Alonzo-Zarazaga and Lyal 1999).
		Thus, four of the five outgroup terminals are represented by species belonging to separate genera in the Tanymecina [non-focal]; viz. Isodacrys buchanani Howden, 1961 [non-focal], Isodrusus debilis Sharp, 1911 [non-focal], Pandeleteinus subcancer Howden, 1969 [non-focal], and Pandeleteius cinereus (Horn, 1876) [non-focal].
		Because generic relationships in the Tanymecini [non-focal] remain unresolved, we selected a relatively far-removed taxon to root the cladogram that would nevertheless display states applicable to the ingroup for characters under consideration (Rieppel 2007; Franz 2014).
		To this end we used the North American species Sitona californicus (Fahraeus, 1840) [non-focal], of the tribe Sitonini Gistel, 1856 [non-focal].

		The character matrix was edited and phylogenetic results viewed using the WinDada and WinClados interfaces of WinClada, respectively (Nixon 2002).
		The character sequence follows that of the taxonomic descriptions.
		The most parsimonious tree and character state optimizations were inferred under parsimony using NONA (Goloboff 1999).
		An unconstrained heuristic search was conducted using the commands: \texttt{hold 100001}, \texttt{mult*1000}, \texttt{hold/100}, with \texttt{mult*max*} selected.
		Bootstrap support was inferred in WinClada using the parameters of \texttt{1000 replications}, \texttt{hold 1000}, \texttt{hold/100}, \texttt{mult*10}, \texttt{Don’t do max*}, and \texttt{Save consensus}.
		Finally, Bremer support values (Bremer 1994) were calculated in NONA using the commands: \texttt{hold 20000}, \texttt{suboptimal 20}, and \texttt{bsupport 20}.

	\paragraph{Species distribution modeling}
		We used the modeling program Maxent, Version 3.4, to generate habitat models for the species of Minyomerus [JF 2015] (Figs.~\#) based on documented occurrence records (Phillips et al. 2004, 2006; Elith et al. 2011).
		The default settings were adjusted to \texttt{Max number background points = 100,000} and \texttt{Iterations = 10}.
		Cross-validation was used to leverage all available locality data; however, no models could be created for species with two or fewer documented localities.
		We selected 19 bioclimatic variables and elevation as Environmental Layers in Maxent, obtained from WorldClim (see Hijmans et al. 2005).
		The layers were downloaded by tile (zones 11–13 and 21–23), with a 30 arc-second resolution (projected using WSG 84) to provide adequate coverage of the full distribution of the genus.
		Layerwise assembly of tiles was done using QGIS, Version 2.18.16 `Las Palmas', creating composite maps of six tiles each to use in species distribution modeling (Quantum GIS Development Team 2017).

		The rasterized predictive probabilities were imported into QGIS, where each file was designated a specific color. 
		Each pixel in the raster was assigned a linearly interpolated saturation of that color, with increasing saturation denoting an increased probability of successful prediction of species presence at that point.
		Pixels with a value below 0.50 were rendered transparent so that the maps only show regions with a greater than 50\% chance of successful prediction.
		The raster files were clipped to remove extraneous predicted regions based on: (1) predictive probability (i.e., removing large areas with only transparent pixels) and (2) geographic extent (accounting for endemicity).
		For example, a species endemic to the Snake River Valley of Idaho does not require a predictive model for bioclimatically similar habitats in the Chihuahuan Desert.
		Documented occurrence records are laid over the modeled habitat ranges as colored circles on their respective maps (Figs.~\#), along with vector layers of country (white) and state (gray) borders (Hijmans et al. 2012).

@@

			\textit{Minyomerus ampullaceus} is best differentiated from other congenerics by its unique body shape, which most prominently features a strongly constricted, sub-cylindrical pronotum and greatly protuberant elytra; this combination gives the species a distinctly flask- or bottle-shaped appearance.
			Due to the relatively poor condition of the scales and setae of the holotype, color and setation cannot be reliably used for identification.
			Fortunately, the elytra themselves are unique in shape, and diagnostic, together nearly 2\x the width of the pronotum at their widest point, and nearly 3/4 as wide as long in dorsal view.
			In lateral view the anterior and posterior declivities of the elytra are strongly abrupt, and nearly vertical; most notably, the anterior magin of the elytra projects strongly and characteristically dorsad of its articulation with the posterior pronotal margin.
			The spermatheca is also quite distinct, having a highly elongate projection of the corpus aligned with midline of the ramus, which is basally tapered and angled at nearly 45\td to the corpus.

@@

			\paragraph{Mandibles}

@@

				Protibia/profemur length ratio \#; protibial apex with ventral setal comb recessed in an incurved groove; mucro present as a large, black, sub-triangular, medially-projected tooth, which is approximately equilateral and whose sides are sub-equal in length to surrounding setae. 

@@

				Length/width ratio \#; widest at anterior 1/3; anterior margins jointly almost 2\x wider than posterior margin of pronotum and strongly produced dorsally from margin of pronotum; lateral margins evenly rounded until posterior 1/3, more strongly rounded and converging thereafter. 

@@

				Comma-shaped; collum expanded to form a long, cylindrical projection, sub-equal in length to ramus, 1/3\x width of corpus, angled at 45\td to corpus, apically with a reduced hood-shaped projection; ramus elongate, bulbous, slightly wider than thickness of corpus, basally constricted to form a short stalk; corpus not greatly swollen; cornu sub-equal in length to corpus and collum, recurved distally to form in inner angle of 60\td to corpus, straight and gradually narrowing along basal 2/3, with apical 1/3 abruptly narrowed, angled at 45\td to coprus, and tapering to a slight knob.

@@

			This species is known only from Carlsbad, New Mexico (USA), from an unspecified locality; the location of the city is shown in Fig.~\#.

@@

			The label indicates ``Geococcyx calif''; this is presumably a reference to \textit{Geococcyx californianus} (Lesson, 1829) [Cuculidae], the Greater Roadrunner, although it is unclear if the specimen was found on or near one of these birds (either living, dead, or in a nest).

@@

			\textit{Minyomerus franko} is readily distinguished from other congenerics by the strikingly long setae of the anterior margin of the pronotum, which project laterally up to 80\td from the longitudinal axis of the body and achieve a maximum length at least equaling the diameter of the eye.
			In addition, the setae lining the dorsal margin of the ocular impression are elongate and reach a length equal to 1/2 - 3/4\x the diameter of the eye.
			The spermatheca has a short, somewhat bulbous corpus, with the ramus sub-equal in size and perpendicular to the corpus, and the collum is strongly recurved along the basal 1/3 of its length.
			The aedeagus is relatively short and wide, and is abruptly constricted in the apical 1/5 of its length, thereafter tapered to a rounded point.

@@

				Protibia/profemur length ratio \#; protibial apex with ventral setal comb recessed in a subtly incurved groove; mucro present as a large, black, sub-triangular, medially-projected tooth, which is approximately equilateral and whose sides are sub-equal in length to surrounding setae. 

@@

				Length/width ratio \#; widest at anterior 1/3-1/4; anterior margins jointly 1.5\x wider than posterior margin of pronotum; lateral margins sub-parallel to slightly rounded after anterior 1/3, more strongly rounded and converging in posterior 1/3. 

@@

			This species has been found in San Luis Potos\'{i} and Tamaulipas (M\'{e}xico).
			It is likely to be found throughout the Chihuahuan Desert and arid regions of south-central M\'{e}xico based on habitat similarity (Fig.~\#).

@@

			\textit{Minyomerus sculptilis} is best distinguished from other congenerics by a combination of characters, as follows.
			The interspersed setae on the body are linear and either brown or white.
			The anterior margin of the pronotum bears a reduced tuft of post-ocular vibrissae.
			The head is barely elevated between the eyes.
			The ventrolateral sulci of  the rostrum are well defined.
			The lateral face of each elytron has the intervals raised and well sculpted in appearance.
			The spermatheca is distinct and has an elongate, annulate, basally tapered ramus, which is slightly thinner than corpus.
			The cornu is strongly recurved in the basal half, giving it a uniquely sinuate appearance.
			Both the corpus and cornu terminate in large, hood-shaped, explanate projections equal in size to the ramus.
			The aedeagus is elongate, acutely angulate, and narrowing towards the apex more strongly in the region of the ostium.

@@

			This species has been found in three localities along the Snake River in Idaho (USA), and is thought to be endemic to the Snake River Valley (Fig.~\#).

@@

			\textit{Minyomerus tylotos} is most readily distinguished from other congenerics by a combination of characters, as follows.
			The nasal plate lacks distinct impressions, having instead a poorly defined anteromesal convexity completely and evenly covered with white scales.
			The frons is protuberant and moderately punctate.
			The entire body, including the legs, head, and venter, are clothed with brown, linear to minutely apically expanded setae, which are of similar length throughout and appear distinctly undifferentiated and uniform across body regions.
			The body is somewhat bulky, with the pronotum protuberant laterally and globular in dorsal view.
			The setae lining the anterodorsal margin of the pronotum uniquely apically explanate, with a longitudinal, medial, ridge-like portion that tapers to either side apicolaterally (visible at high magnification).
			The lateral margins of the elytra are protuberant anteriorly and sub-parallel along the between anterior 1/5 and posterior 1/3 of their length.
			The spermatheca has the corpus narrow throughout, equal in thickness to the collum.
			The ramus is basally stalked and apically bulbous.
			The collum exhibits a double-bend, and is recurved.

@@

				Stipes sub-rectangular, 1.5\x wider than long, roughly equal in width to inner arm of bifurcation of cardo, glabrous. 

@@

				Rostrum ventrally with sub-parallel sulci beginning at corners of oral cavity and continuing halfway to back of head.

@@

				Pronotum in lateral view with transverse ventrolateral sulci strongly excavated and distinctly sculptured; with short, recumbent to sub-erect setae that barely attain or reach just beyond anterior margin; these setae becoming shorter and more erect laterally, reaching a maximum length nearly equal to length of eye; dorsally, these setae become uniquely apically explanate, with a longitudinal, medial, ridge-like portion that tapers to either side apicolaterally.

@@

				Length/width ratio \#; widest at anterior 1/6; anterior margins jointly 1.5-2\x wider than posterior margin of pronotum; lateral margins nearly straight and sub-parallel after anterior 1/5, converging in posterior 1/3. 

@@

			This species has been found in three localities near the Davis Mountains in Jeff Davis County and in nearby Presidio County, Texas (USA).
			Habitat models (Figs.~\#) predict that this represents the northeastern extent of its range, indicating a strong likelihood that it is present in other parts of the northern Chihuahuan desert, especially in the state of Chihuahua (M\'{e}xico).

@@

\section*{Checklist of species}
	\begin{tabbing}
		\quad \= \quad \= = \= \kill
		\textit{Minyomerus} Horn, 1876: 17\\
				\> \> = \textit{Elissa} Casey, 1888: 271\\
				\> \> \> (synonymized by Kissinger, 1964: 30)\\
				\> \> = \textit{Pseudelissa} Casey, 1888: 273\\
				\> \> \> (synonymized by Pierce, 1909: 359)\\
				\> \> = \textit{Piscatopus} Sleeper, 1960: 84\\
				\> \> \> (synonymized by Jansen and Franz, 2015: 12)\\
			\> \textit{microps} (Say, 1831: 9) [redescribed by Jansen and Franz, 2015: 45]\\
				\> \> = \textit{Minyomerus innocuus} Horn, 1876: 18\\
				\> \> \> [former type of \textit{Minyomerus}, designated by Pierce, 1913: 400]\\
				\> \> \> (synonymized by Jansen and Franz, 2015: 45)\\
				\> \> = \textit{Thylacites microps} Say, 1831: 9\\
				\> \> \> (transferred to \textit{Minyomerus} on the authority of Buchanan \textit{in litt.}\\
				\> \> \> by Blackwelder and Blackwelder, 1948: 46)\\
				\> \> = \textit{Thylacites microsus} Boheman, 1833: 523\\
				\> \> \> (synonymized by LeConte, 1859: 286)\\
			\> \textit{aeriballux} Jansen and Franz, 2015: 52\\
			\> \textit{ampullaceus} \textbf{sp. nov.}\\
			\> \textit{bulbifrons} Jansen and Franz, 2015: 81\\
			\> \textit{caseyi} (Sharp, 1891: 151) [redescribed by Jansen and Franz, 2015: 66]\\
				\> \> = \textit{Pseudelissa caseyi} Sharp, 1891: 151\\
				\> \> \> (genus synonymized by Pierce, 1909: 359)\\
			\> \textit{conicollis} Green, 1920: 194 [redescribed by Jansen and Franz, 2015: 33]\\
			\> \textit{constrictus} (Casey, 1888: 272) [redescribed by Jansen and Franz, 2015: 22]\\
				\> \> = \textit{Elissa constricta} Casey, 1888: 272\\
				\> \> \> (genus synonymized by Kissinger, 1964: 30)\\
			\> \textit{cracens} Jansen and Franz, 2015: 61\\
			\> \textit{franko} \textbf{sp. nov.}\\
			\> \textit{gravivultus} Jansen and Franz, 2015: 92\\
			\> \textit{griseus} (Sleeper, 1960: 84) [redescribed by Jansen and Franz, 2015: 96]\\
				\> \> = \textit{Piscatopus griseus} Sleeper, 1960: 84\\
				\> \> \> (genus synonymized by Jansen and Franz, 2015: 96)\\
			\> \textit{imberbus} Jansen and Franz, 2015: 18\\
			\> \textit{languidus} Horn, 1876: 18 [redescribed by Jansen and Franz, 2015: 40]\\
				\> \> = \textit{Pseudelissa cinerea} Casey, 1888: 274\\
				\> \> \> (synonymized by Pierce, 1909: 359)\\
			\> \textit{laticeps} (Casey, 1888) [redescribed by Jansen and Franz, 2015: 27]\\
				\> \> = \textit{Elissa laticeps} Casey, 1888: 272\\
				\> \> \> (genus synonymized by Kissinger, 1964: 30)\\
			\> \textit{politus} Jansen and Franz, 2015: 86\\
			\> \textit{puticulatus} Jansen and Franz, 2015: 75\\
			\> \textit{reburrus} Jansen and Franz, 2015: 57\\
			\> \textit{rutellirostris} Jansen and Franz, 2015: 103\\
			\> \textit{sculptilis} \textbf{sp. nov.}\\
			\> \textit{trisetosus} Jansen and Franz, 2015: 71\\
			\> \textit{tylotos} \textbf{sp. nov.}\\
	\end{tabbing}

\section*{Identification key}
	\#
\section*{Phylogenetic placement of new species}
	\#
\section*{Acknowledgments}
